Final project

### 2025-04-06 products/manuscript/Manuscript.qmd
Finalizing changes

# Load necessary libraries
```{r}
library(knitr)
library(readr)
library(dplyr)
library(ggplot2)
library(ggcorrplot)
library(vcd)
library(caret)        # For data partitioning and model training
library(randomForest) # For Random Forest modeling
library(tidyverse)
library(tidymodels)
library(broom)
library(here)           # For file paths
library(pROC)
library(naniar)         # For gg_miss_var()
```

# PART 1: DATA IMPORT AND CLEANING
```{r}
# Import the dataset
cardio_df <- read_csv(here("data", "raw-data", "Cardiovascular_Disease_Dataset.csv"))

@@

# Fit a logistic regression model including the interaction term
model_interaction <- glm(target_binary ~ elevated_BP * elevated_oldpeak, 
                         data = cleaned_df, family = binomial)
summary(model_interaction)
```

@@

@@

```{r}
rr_model <- glm(target_binary ~ elevated_BP + elevated_oldpeak, 
                data = cleaned_df, family = binomial(link = "log"))
rr_values <- exp(coef(rr_model))
rr_ci <- exp(confint(rr_model))
rr_results <- data.frame(
  Term = names(rr_values),
  RR = rr_values,
  CI_lower = rr_ci[, 1],
  CI_upper = rr_ci[, 2]
)
print("Relative Risks (with 95% CI):")
print(rr_results)
```

@@

>>>>

# Load necessary libraries

```{r}
library(knitr)
library(readr)
library(dplyr)
library(ggplot2)
library(ggcorrplot)
library(vcd)
library(caret)        # For data partitioning and model training
library(randomForest) # For Random Forest modeling
library(tidyverse)
library(tidymodels)
library(broom)
library(here)           # For file paths
library(pROC)
library(naniar)         # For gg_miss_var()
```

# PART 1: DATA IMPORT AND CLEANING

```{r}
# Import the dataset
cardio_df <- read_csv(here("data", "raw-data", "Cardiovascular_Disease_Dataset.csv"))

@@

# save fit results table  
table_file1 = here("results", "tables", "resulttable1.rds")
saveRDS(model, file = table_file1)

# Fit a logistic regression model including the interaction term
model_interaction <- glm(target_binary ~ elevated_BP * elevated_oldpeak, 
                         data = cleaned_df, family = binomial)
summary(model_interaction)

# save fit results table  
table_file1 = here("results", "tables", "resulttable2.rds")
saveRDS(model_interaction, file = table_file1)
```

@@

# save fit results table  
table_file1 = here("results", "tables", "resulttable3.rds")
saveRDS(or_results, file = table_file1)

@@

```{r}
rr_model <- glm(target_binary ~ elevated_BP + elevated_oldpeak, 
                data = cleaned_df, family = binomial(link = "log"))
rr_values <- exp(coef(rr_model))
rr_ci <- exp(confint(rr_model))
rr_results <- data.frame(
  Term = names(rr_values),
  RR = rr_values,
  CI_lower = rr_ci[, 1],
  CI_upper = rr_ci[, 2]
)
print("Relative Risks (with 95% CI):")
print(rr_results)

# save fit results table  
table_file1 = here("results", "tables", "resulttable4.rds")
saveRDS(rr_results, file = table_file1)
```

@@

# save fit results table  
table_file1 = here("results", "tables", "resulttable5.rds")
saveRDS(adj_or_results, file = table_file1)
